\newcommand{\award}[4]
{
    {\fontseries{b} \normalsize #1 \hfill #4 }

    {\small #2}\\
    {\footnotesize Awarded by #3}
    \sepspace
}

\def \awards
{
    \award  {University Medal}
            {For being the most outstanding student in the Faculty of Science, Engineering and Technology in 2016.}
            {Graham Goldsmith -- Chancellor, Swinburne University.}
            {28 August 2017}

    \award  {Swinburne Computer Science and Software Engineering Prize}
            {In recognition of the highest achieving graduate in the BSc. (Software Development) in 2016.}
            {Prof. Linda Kristjanson -- Vice Chancellor, Swinburne University.}
            {31 May 2017}

    \award  {Integrated Application Development James Wauchope Prize}
            {In recognition of the highest achieving graduate in the BSc. (Software Development) in 2016.}
            {Prof. Linda Kristjanson -- Vice Chancellor, Swinburne University.}
            {31 May 2017}

    \award  {Pham Family Honours Scholarship}
            {For a high achieving student commencing the BIT (Honours) in 2017.}
            {Prof. Trevor Day -- Executive Dean, Deakin University.}
            {5 Apr 2017}
    \clearpage        
    \award  {Deakin Scholarship of Excellence}
            {For demonstrating exceptional promise beyond academic achievements.}
            {Deakin University.}
            {1 Mar 2017}
            
    \award  {2016 Swinburne Student Achievement Award}
            {For demonstrating a high level capacity to be flexible, adaptable and in overcoming life's challenges in order to meet study commitments.}
            {Swinburne University.}
            {Sep 2016}
    
    \award  {Certificate of Achievement Awards}
            {Highest Achieving Student with the highest marks in nine subjects.}
            {Prof. John Wilson -- Executive Dean, Swinburne University.}
            {Nov 2014, Jul 2015}

    \award  {Certificate of Appreciation Award}
            {Swinburne ICT Student Ambassador Program.}
            {Prof. Leon Sterling -- Dean, Swinburne University.}
            {1 Nov 2013}

    \award  {Vice Chancellor's Scholarship}
            {On outstanding academic excellence.}
            {Prof. Linda Kristjanson -- Vice Chancellor, Swinburne University.}
            {31 Mar 2013}

    \award  {Dux Award}
            {On excellent VCE results and one of the highest ATAR scores in the college.}
            {Dr. Denis Moore -- Principal, Parade College.}
            {8 Feb 2013}
}
