\newcommand{\job}[6]
{
    {\fontseries{b} \normalsize #1 \hfill {#2}--{#3}}\\
    {
        \small
        #4\\
        {\footnotesize #5}
        \begin{itemize}
            #6
        \end{itemize}
    }
    \sepspace
}

\def \experience
{
    \job{Software Engineer and Research Assistant}
        {Dec 2016}{Present}
        {Deakin Software and Technology Innovation Laboratory (DSTIL), Burwood}
        {\href{http://www.deakin.edu.au/information-technology/dstil}{DSTIL} produces innovative products, technologies and software solutions across all sectors.}
        {
          \item Researched a data engineering pipeline to detect alphanumeric sequences in unstructured scenes via neural networks.
          \item Development of image annotation software to assist with curating data to be feed into artificial intelligence models.
          \item Worked on developing on a new online platform to support e-learning at Deakin University.
        }
    \job{Tutor}
        {Aug 2017}{Present}
        {International House, The University of Melbourne, Parkville}
        {Non-residential tutor focusing on teaching second-year \href{https://handbook.unimelb.edu.au/2017/subjects/swen20003}{object-oriented programming} using Java.}
        {
            \item Supplement student knowledge by exposing them to core OOP concepts.
            \item Provide further examples in various languages to broaden language exposure.
            \item Help prepare students for tests and exams.
            \item Assist students with weekly programming tasks and assignments.
        }

    \job{Tutor}
        {Mar 2017}{Jun 2017}
        {Deakin University, Burwood}
        {Teaching a first-year \href{http://www.deakin.edu.au/current-students-courses/unit.php?unit=SIT120}{Introduction to Apps Design} unit.}
        {
          \item Introduce app development concepts, such as monetisation and development lifecycles.
          \item Develop app prototypes using via mobile-friendly web applications.
          \item Introduce students to HTML5, CSS, JavaScript, jQuery and DOM manipulation.
          \item Encourage group discussion with students and pairing exercises.
        }
    \clearpage
    \job{iOS Developer}
        {Aug 2015}{Feb 2016}
        {SEEK Ltd., Melbourne}
        {\href{http://seek.com.au}{SEEK} is Australia's largest jobs, employment, career and recruitment website.}
        {
          \item Development and release of the SEEK jobseeker \href{https://itunes.apple.com/us/app/seek-jobs/id520400855?mt=8}{iPhone and iPad app} app.
          \item Integrated a prompt for app feedback review, which improved the App Store rating from six 1 star reviews to 33 reviews averaging 4.5 stars on launch-day alone.
          \item Added personal recommendations to the jobseeker app, providing thousands of personalised jobs to candidates on their mobiles.
          \item Experience with continuous deployment and test-driven development environments.
        }
    \job{Software Engineer}
        {Aug 2014}{Aug 2015}
        {Swinburne NICTA Software Innovation Lab (SSIL), Hawthorn}
        {SSIL delivers research-driven high-impact software solutions and is partnered with NICTA.}
        {
          \item Lead drone-flight software project that automates drone flights.
          \item Developed fleet visualiser prototype integrated using Google Maps SDK used for bus fleets in Kuala Lumpur.
          \item Created a \href{http://rappt.io/}{web-based IDE} used for rapid prototyping software to create Android apps.
          \item Development with bleeding-edge technology stacks and rapid-prototyping environment.
        }
    \job{Tutor}
        {Mar 2014}{Aug 2016}
        {Swinburne University of Technology, Hawthorn}
        {\href{http://www.swinburne.edu.au/study/courses/units/Introduction-to-Programming-COS10009/local}{Teaching first-year introductory programming} \href{http://www.swinburne.edu.au/study/courses/units/Object-Oriented-Programming-COS70006/local}{and object-oriented programming units}.}
        {
          \item Engagingly teaching students to learn foundation programming concepts.
          \item Group discussion and running group exercises.
          \item Preparing students for future programming and problem-solving units.
          \item Helping students through basic Pascal, C and \Csh\hspace{0.25ex}and giving one-to-one feedback.
        }
    \job{Freelance UI/UX Designer}
        {Mar 2014}{Aug 2016}
        {LeadSoftware, Melbourne}
        {\href{http://www.leadsoftware.com.au/}{LeadSoftware specialises in complete tracking, logistic and dispatch systems.}}
        {
          \item Lead UX and UI design for FairFind, a global marketplace for antique, fashion, fine art and collectable fairs.
          \item Lead UX and UI design for a large-scale on-board taxi dispatch system and iOS/Android apps in development for CABiT, a Melbourne-based Taxi company.
          \item Strong interaction with development team to explain prototypes and mock-ups developed and provide feedback on implemented designs.
          \item Iterative prototype process using a mix of whiteboard, Pixelmator, Keynote and FluidUI.
        }
    % \job{Web Application Developer (Pro Brono)}
    %     {Winter Break}{2014}
    %     {Swinburne University of Technology, Hawthorn}
    %     {\href{http://alexcu.me/#modal-doubtfire}{Development of a lightweight modern Learning Management System, \emph{Doubtfire}.}}
    %     {
    %         \item Building a large-scale web application utilised in tutoring position for student progress tracking (\href{http://github.com/doubtfire-lms}{http://github.com/doubtfire-lms})
    %         \item Developing front-end development with Bootstrap and AngularJS
    %         \item Back-end development using Ruby on Rails, PostGres and Grape API
    %     }
    % \job{Programming Help Desk Staff}
    %     {Aug 2013}{Dec 2013}
    %     {Swinburne University of Technology, Hawthorn}
    %     {Providing assistance in out-of-class sessions with students.}
    %     {
    %         \item Assisting students learn syntax of C, Pascal, PHP, JavaScript
    %         \item Explaining programming concepts to students and working through logic problems in a enthusiastic and approachable environment
    %         \item Help Desk initiative and staff commended by the Australian Computer Society
    %     }
    % \job{Cashier}
    %     {Apr 2011}{Dec 2013}
    %     {Target Australia Pty. Ltd, Northland Shopping Centre}
    %     {
    %         \item Managing peak shopping periods, working through Boxing Day and Easter Sales.
    %         \item Adapting to varying roles in the store during off-periods.
    %         \item Customer service management and sharing knowledge of products with customers.
    %         \item Working together with other team members to get through day-to-day operational activities
    %     }
}
